%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


\documentclass[12pt, a4paper]{awesome-cv}
\geometry{left=2cm, top=2cm, right=2cm, bottom=1.7cm, footskip=.5cm}
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-darknight}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{false}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}
\usepackage{xcolor}

% Available options: circle|rectangle,edge/noedge,left/right
% \photo{./profile.png}
%\name{Yash}{Srivastav}
%\position{Senior Undergraduate{\enskip\cdotp\enskip}Computer Science and Engineering}
%\address{Indian Institute of Technology, Kanpur}
%\mobile{(+91) 705-413-3662}
%\email{yash111998@gmail.com}
%\homepage{yashsriv.org}
%\github{yashsriv}
%\linkedin{yashsriv}
% \twitter{@therealyashsriv}
% \quote{``There is no fate but what we make."}

\newcommand{\smallcventry}[6]{\cventry{#1}{#2}{#3}{#4}{#6}}
\newcommand{\specialcvsection}[1]{\cvsection{#1}}




\begin{document}
%\makecvheader
\makecvfooter
  {}
  {}
  {\thepage}
\begin{minipage}[t]{\textwidth}
	{\Huge\textbf{\sc Shivam Kumar}}
	\hfill
	shivamkm07@gmail.com \faEnvelope\\	
	Final Year Undergraduate
	\hfill
	\href{https://github.com/shivamkm/}{shivamkm \faGithub}
	\\	
	Department of Computer Science and Engineering
	\hfill
	\href{https://www.linkedin.com/in/shivamkm07/}{shivamkm07 \faLinkedin}\\
	%+91-7054133662 \faMobile \\
	Indian Institute of Technology, Kanpur
	\hfill +91-9129085031 \faMobile
	%+91-7054133662 \faMobile \\
\end{minipage}
\\\\


{\color{blue}To:\\}
Tanmay Gopal\\
CEO, Hasura

\hfill{\color{gray}October 16, 2020}

Subject: \textbf{Application for Software Engineer Position}\\

Dear Mr. Gopal,
	
	I am a final year undergraduate at IIT Kanpur, majoring in Computer Science \& Engineering. Please consider my application for software engineer position at Hasura.
	
	I have explored several sectors of Computer Science during my stay at IITK, the notable ones being Parallel Programming, Cryptography, Functional Programming(Haskell), Propositional logic etc. 
		
	I have worked extensively for nearly an year on Data Race Detection in Task-Parallel Programs and came up with a novel race-checking algorithm called {\sc{Tusker}}. It is found to incur significantly low space as well as time overheads, performing better than all other SOTA in the same domain. I have also dealt with several of the standard parallel libraries including Pthread, Intel TBB and OpenMP.
	
	With regard to my ability to meet specific requirements for the job:
	\begin{itemize}
		\item \textbf{Language}: C/C++(Proficient), Python(Proficient), Haskell(Moderate), Java(Moderate), PHP(Basic), JavaScript(Basic)
		
		\item \textbf{CS Fundamentals}: Sufficient knowledge of CS basics like Compilers, Operating Systems, Algorithms, DataBases etc. 
		
		\item \textbf{Engineering Aptitude}: Experience with several tools including MySql, MongoDB, LLVM, TensorFlow etc.
	
	\end{itemize}
	
	
	I have also implemented several of the key projects in different fields including designing java compiler using PLY, implementing decoder for several popular ciphers, building a fully-functional MERN application etc.
%	
%	I have always aspired to be the part of a dedicated engineering team employing several key technologies to build products. Hasura completely fits in my aspirations and therefore working here is something that I definitely look forward to.
%	

	There must be several applications for the same. However, I do believe that with my keen interest in working around the latest technologies, pre-existing skills and perseverance, I can be an integral part of Hasura.
	
	I, therefore, sincerely request you to consider my application for the role and give me an opportunity for proving myself. I have attached my resume and gradesheet with the application.\\\\
	
	Thanking you for your valuable time.
	
	Regards,\\
	Shivam
	
	
	
	%\input{sections/education.tex}
%\input{sections/academic.tex}
%\input{sections/experience.tex}
%\input{sections/skills.tex}
%\input{sections/coursework.tex}
%\newpage
%\input{sections/project.tex}
%\input{sections/positions.tex}
%\input{sections/misc.tex}
% \input{sections/interests.tex}


\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-engine: xetex
%%% End: