%-------------------------
% Resume in LaTeX
% Based on: https://github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[a4paper,9pt]{extarticle}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure PDF is machine readable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small #1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small #1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItemPlain{#1}\vspace{-4pt}}

\newcommand{\resumeItemPlain}[1]{
  \item\small{#1 \vspace{-3pt}}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Shivam Kumar} \\ \vspace{1pt}
    \small
    \href{tel:+919129085031}{+91-9129085031} \,$\vcenter{\hbox{\footnotesize\faMobile}}$
    $|$
    \href{mailto:shivamkm07@gmail.com}{shivamkm07@gmail.com} \,$\vcenter{\hbox{\footnotesize\faEnvelope}}$
    $|$
    \href{https://www.linkedin.com/in/shivamkm07}{linkedin.com/in/shivamkm07} \,$\vcenter{\hbox{\footnotesize\faLinkedin}}$
    $|$
    \href{https://github.com/shivamkm07}{github.com/shivamkm07} \,$\vcenter{\hbox{\footnotesize\faGithub}}$
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology, Kanpur}{CGPA: 9.4/10.0}
      {Bachelor of Technology in Computer Science and Engineering}{2017 -- 2021}
    \resumeSubheading
      {Sunbeam English School, CBSE}{96.4\%}
      {AISSCE (Class XII)}{2017}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Development Engineer II}{Jul 2024 -- Present}
      {Microsoft -- Azure Container Apps}{Hyderabad, India}
      \resumeItemListStart
        \resumeItemPlain{Designed and deployed \textbf{AI-powered SRE agents} for Azure Container Apps incident diagnostics, reducing P50 time-to-mitigate by \textbf{97\% (185$\rightarrow$6 min)} and time-to-resolve by \textbf{64\%}; evolving toward \textbf{autonomous auto-repair} with automated RCA comparison; enabled \textbf{Foundry Control Plane} for ACA-hosted agents.}
        \resumeItemPlain{Built \textbf{Session Management APIs} and fixed critical async execution bugs for ACA Sessions, improving stability for \textbf{$\sim$300 external customers}; enabled early session deletion for the Fabric team, optimizing billing and costs.}
        \resumeItemPlain{Expanded \textbf{Azure Functions on ACA} platform --- function keys management, invocation tracing, durable-events logging, KEDA scaling rules, and drain functionality, benefiting \textbf{$\sim$1,322 external apps}.}
        \resumeItemPlain{Led \textbf{Dapr AKS Extension} rollouts (v1.15, v1.16) across all Azure regions; remediated CVEs across \textbf{$\sim$400 AKS clusters}; integrated CodeQL for pipeline security.}
        \resumeItemPlain{Integrated \textbf{Azure Key Vault} with Managed Environment Storage API, securing \textbf{$\sim$27K daily API calls} by eliminating raw connection strings.}
        \resumeItemPlain{Served as \textbf{on-call DRI} resolving \textbf{200+ incidents} including 27+ CRIs, outperforming team baselines.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Development Engineer}{Jul 2021 -- Jul 2024}
      {Microsoft -- Azure Container Apps / Dapr}{Hyderabad, India}
      \resumeItemListStart
        \resumeItemPlain{Contributed to \textbf{Dapr} (CNCF open-source project) --- improved several components and APIs to stable; implemented \textbf{cascade terminate/purge} for Dapr Workflows across runtime and SDKs; added bulk subscribe support in Azure Event Hubs; added workflow performance tests identifying P0 bugs.}
        \resumeItemPlain{Enabled \textbf{airgap installation}, winget, and MSI for Dapr CLI; published combined coverage reports; resolved customer issues on GitHub and Discord.}
        \resumeItemPlain{Architected \textbf{internal fork and CI/CD infrastructure} across 5 Dapr repositories; automated OSS-to-internal releases within \textbf{$<$1 day SLA}; consolidated into \textbf{OneBranch-compliant} pipelines with Ev2 deployment.}
        \resumeItemPlain{Added \textbf{multi-arch support} (ARM64, ARM, AMD64), Mariner and distroless images; handled 1P Container Registry migration; delivered nightly builds for ACA; contributed to AKS Extension GA requirements.}
        \resumeItemPlain{Helped launch \textbf{ACA Sessions public preview} --- added support for Node.js code interpreter sessions; fixed critical bugs in Python and Node.js sessions; added performance tests identifying regressions.}
      \resumeItemListEnd

    \resumeSubheading
      {Quantitative Research Intern}{May 2020 -- Jul 2020}
      {JP Morgan \& Chase -- E-Trading}{Mumbai, India (Remote)}
      \resumeItemListStart
        \resumeItemPlain{Built price prediction models using \textbf{LSTM}, feedforward neural networks, and regression with univariate feature selection.}
        \resumeItemPlain{Improved model predictive power by \textbf{40\%} for HK names through feature standardization and data preprocessing.}
        \resumeItemPlain{Implemented L1 and L2 features for optimizing model parameterization across multiple asset classes.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------RESEARCH-----------
\section{Research}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Data Race Detection for Task-Parallel Programs}{Jun 2019 -- Aug 2021}
      {Supervisor: Prof. Swarnendu Biswas, IIT Kanpur}{}
      \resumeItemListStart
        \resumeItemPlain{Designed novel algorithm \textbf{Tasker} integrating vector clocks with tree-based techniques; implemented using \textbf{LLVM} pass for memory instrumentation on task-parallel programs.}
        \resumeItemPlain{Achieved \textbf{1.48X speedup} over PTRacer baseline on 128GB Intel Xeon system with lower memory overhead.}
        \resumeItemPlain{\textit{``Efficient Data Race Detection of Structured Task Parallel Programs Using Vector Clocks''} --- S.~Kumar, A.~Agrawal, S.~Biswas $|$ Submitted to ISCGO 2022.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\href{https://github.com/shivamkm/java-compiler}{\textbf{Java Compiler}} $|$ \emph{Python, PLY, Compiler Design (CS335)}}{Jan 2020 -- Apr 2020}
      \resumeItemListStart
        \resumeItemPlain{Designed lexer, parser, and 3-address code generation; support for symbol tables, classes, functions, and interfaces.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\href{https://github.com/shivamkm/gemOS}{\textbf{GemOS}} $|$ \emph{C, x86, Operating Systems (CS330)}}{Aug 2019 -- Nov 2019}
      \resumeItemListStart
        \resumeItemPlain{Implemented mmap, munmap, mprotect with lazy allocation and pagefault handling; cfork/vfork with copy-on-write.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\href{https://github.com/shivamkm/machine-learning}{\textbf{Machine Learning}} $|$ \emph{Python, Keras, ML (CS771)}}{Aug 2019 -- Nov 2019}
      \resumeItemListStart
        \resumeItemPlain{CNN image classification using Keras; SGD for binary classification; multi-label Bonsai recommender system.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\href{https://github.com/shivamkm/decipher}{\textbf{Cipher Decoder}} $|$ \emph{Python, Modern Cryptology (CS641)}}{Aug 2020 -- Nov 2020}
      \resumeItemListStart
        \resumeItemPlain{Differential cryptanalysis of 3-DES; decryption of Caesar, Vigenere ciphers using frequency analysis.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\href{https://github.com/shivamkm/sat-solver}{\textbf{SAT Solver}} $|$ \emph{Python, Logic in CS (CS202)}}{Jan 2019 -- Apr 2019}
      \resumeItemListStart
        \resumeItemPlain{DPLL-based SAT solver; encoded diagonal sudoku constraints in DIMACS propositional logic format.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\href{https://github.com/shivamkm/mobile-app}{\textbf{MERN Mobile App}} $|$ \emph{React Native, Node.js, MongoDB (CS252)}}{May 2019 -- Jul 2019}
      \resumeItemListStart
        \resumeItemPlain{Full-stack mobile app with React Native frontend, Node.js/Express backend, MongoDB, and secure JWT login.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Go, Python, C\#/.NET, JavaScript/TypeScript, C/C++} \\
     \textbf{Cloud \& Infrastructure}{: Azure (Container Apps, AKS, Functions, Key Vault, Event Hubs, CosmosDB), Kubernetes, Docker, Dapr (CNCF), Helm} \\
     \textbf{Tools \& CI/CD}{: OneBranch (1ES), Ev2, Azure DevOps Pipelines, GitHub Actions, Git, Geneva, CodeQL, KEDA} \\
     \textbf{Domains}{: Distributed Systems, AI/LLM Agents, CI/CD \& Release Engineering, Microservices, Site Reliability (SRE)}
    }}
 \end{itemize}

%-----------ACHIEVEMENTS-----------
\section{Achievements \& Leadership}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{RockStar Award}, Microsoft ('22, '23) for exceptional contributions $|$ \textbf{Academic Excellence Award} ($\times$2), IIT Kanpur \\
      JEE Advanced \textbf{AIR 715} $|$ JEE Mains \textbf{AIR 348} $|$ KVPY Scholar $|$ NSE Physics \textbf{Top 1\%} $|$ Ram Prakash Chopra Scholarship \\
      Academic Mentor, IIT Kanpur ('18-19) $|$ Secretary, Dramatics Club, IIT Kanpur ('18-19)
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
