%-------------------------
% Resume in LaTeX
% Based on: https://github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[a4paper,9pt]{extarticle}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure PDF is machine readable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small #1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small #1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItemPlain{#1}\vspace{-4pt}}

\newcommand{\resumeItemPlain}[1]{
  \item\small{#1 \vspace{-3pt}}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Shivam Kumar} \\ \vspace{1pt}
    \small
    \href{tel:+919129085031}{+91-9129085031} \,$\vcenter{\hbox{\footnotesize\faMobile}}$
    $|$
    \href{mailto:shivamkm07@gmail.com}{shivamkm07@gmail.com} \,$\vcenter{\hbox{\footnotesize\faEnvelope}}$
    $|$
    \href{https://www.linkedin.com/in/shivamkm07}{linkedin.com/in/shivamkm07} \,$\vcenter{\hbox{\footnotesize\faLinkedin}}$
    $|$
    \href{https://github.com/shivamkm07}{github.com/shivamkm07} \,$\vcenter{\hbox{\footnotesize\faGithub}}$
\end{center}

%-----------SUMMARY-----------
\section{Summary}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Software Development Engineer II at Microsoft (Azure Container Apps) with 5+ years building cloud-native platforms, AI-powered SRE agents, and CNCF open-source infrastructure (Dapr). Designed RCA agents that cut P50 incident time-to-mitigate by \textbf{97\%} (185$\rightarrow$6 min) --- squad won \textbf{IDC Pinnacle FY'26 best AI success story award} ($\sim$200+ teams); drove \textbf{ACA Express Public Preview} enablement on ADC targeting \textbf{$\sim$\$40M annual COGs savings}; shipped \textbf{Foundry Control Plane integration} for $\sim$2K agentic apps; architected internal forks and OneBranch/Ev2 pipelines for 5 Dapr repos with \textbf{$<$1 day OSS release SLA}. \\
     \vspace{2pt}
     \textbf{Focus}{: Distributed Systems $\cdot$ AI/LLM Agents \& AI-Augmented Engineering $\cdot$ Site Reliability (SRE) $\cdot$ CI/CD \& Release Engineering $\cdot$ Kubernetes \& Container Platforms}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Development Engineer II}{Jul 2024 -- Present}
      {Microsoft -- Azure Container Apps}{Hyderabad, India}
      \resumeItemListStart
        \resumeItemPlain{Designed and deployed \textbf{AI-powered SRE agents} for ACA --- reduced P50 time-to-mitigate by \textbf{97\% (185$\rightarrow$6 min)} and time-to-resolve by \textbf{64\%}; sustained \textbf{$\sim$99\% RCA coverage} with \textbf{$\sim$76\% on-call accuracy}, \textbf{auto-resolving 57 of $\sim$400 CRIs} and authoring \textbf{$\sim$132 repair items} in 6 months; stood up Ev2 release pipeline. Squad won \textbf{IDC Pinnacle FY'26 best AI success story} ($\sim$200+ teams).}
        \resumeItemPlain{Drove \textbf{ACA Express Public Preview} enablement on \textbf{Azure Dev Compute (ADC)} --- closed P0 gaps via \textbf{ephemeral volume support} and \textbf{Log Analytics customer-log delivery} landing on both ADC and ACA; migration path for \textbf{$\sim$100K+ ACA environments}, targeting \textbf{$\sim$\$40M annual COGs savings}.}
        \resumeItemPlain{Designed and shipped \textbf{Foundry Control Plane integration} for ACA --- new preview API across clouds, Control Plane, and CRD; supports customer-declared and auto-detection modes; covers \textbf{$\sim$2,000+ agentic apps}, making ACA a first-class hosting target for Foundry agents.}
        \resumeItemPlain{Built \textbf{Session Management APIs} and fixed critical async execution bugs for ACA Sessions, improving stability for \textbf{$\sim$300 external customers}; enabled early session deletion for the Fabric team, optimizing billing and costs.}
        \resumeItemPlain{Stabilized \textbf{Azure Functions on ACA} ($\sim$5K managed + $\sim$1,322 external apps) --- shipped \textbf{graceful drain} (retired 3 recurring CRIs), queueLength/scale-rule overrides, JWT clock-skew leeway, function keys management, and KEDA scaling rules; migrated Functions telemetry to \textbf{central capps Kusto clusters}, unblocking alerting and agent skills.}
        \resumeItemPlain{Led \textbf{Dapr AKS Extension} rollouts (v1.15, v1.16) across all Azure regions with daily artifact refresh; remediated CVEs across \textbf{$\sim$400 AKS clusters} and integrated CodeQL; integrated \textbf{Azure Key Vault} with Managed Environment Storage API, securing \textbf{$\sim$27K daily API calls} by eliminating raw connection strings.}
        \resumeItemPlain{Served as \textbf{on-call DRI} across multiple rotations resolving \textbf{240+ incidents (65+ CRIs, 36 Sev2 LSIs)} --- P50 TTM 1h / TTR 25h vs ACA 3.9h/60h baselines; delivered repair items reducing recurrence; mentored 2 new hires through first on-call rotations.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Development Engineer}{Jul 2021 -- Jul 2024}
      {Microsoft -- Azure Container Apps / Dapr}{Hyderabad, India}
      \resumeItemListStart
        \resumeItemPlain{Contributed to \textbf{Dapr} (CNCF) --- upgraded MQTT PubSub, CosmosDB, Redis/PostgreSQL stores, and Configuration API to stable; implemented \textbf{cascade terminate/purge} for Dapr Workflows across runtime and SDKs; added bulk subscribe in Azure Event Hubs and workflow perf tests identifying P0 bugs.}
        \resumeItemPlain{Enabled \textbf{airgap installation}, winget, and MSI for Dapr CLI; published combined coverage reports; resolved customer issues on GitHub and Discord.}
        \resumeItemPlain{Architected \textbf{internal fork and CI/CD infrastructure} across 5 Dapr repositories; automated OSS-to-internal releases within \textbf{$<$1 day SLA}; consolidated into \textbf{OneBranch-compliant} pipelines with Ev2 deployment.}
        \resumeItemPlain{Added \textbf{multi-arch support} (ARM64, ARM, AMD64), Mariner and distroless images; handled 1P Container Registry migration; delivered nightly builds for ACA; contributed to AKS Extension GA requirements.}
        \resumeItemPlain{Helped launch \textbf{ACA Sessions public preview} --- added Node.js code interpreter support; fixed critical Python/Node.js session bugs; added performance tests identifying regressions.}
      \resumeItemListEnd

    \resumeSubheading
      {Quantitative Research Intern}{May 2020 -- Jul 2020}
      {JP Morgan \& Chase -- E-Trading}{Mumbai, India (Remote)}
      \resumeItemListStart
        \resumeItemPlain{Built price prediction models using \textbf{LSTM}, feedforward neural networks, and regression with univariate feature selection; improved predictive power by \textbf{40\%} for HK names through feature standardization.}
        \resumeItemPlain{Implemented L1 and L2 features for optimizing model parameterization across multiple asset classes.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Go, Python, C\#/.NET, JavaScript/TypeScript, C/C++} \\
     \textbf{Cloud \& Infrastructure}{: Azure (Container Apps, AKS, Functions, Key Vault, Event Hubs, CosmosDB), Kubernetes, Docker, Dapr (CNCF), Helm} \\
     \textbf{Tools \& CI/CD}{: OneBranch (1ES), Ev2, Azure DevOps Pipelines, GitHub Actions, Git, Geneva, Kusto/ADX, CodeQL, KEDA, Argus} \\
     \textbf{Domains}{: Distributed Systems, AI/LLM Agents, AI-Augmented Engineering (Copilot review skills, e2e stamp validation), Site Reliability (SRE), CI/CD \& Release Engineering}
    }}
 \end{itemize}

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\href{https://github.com/shivamkm/gemOS}{\textbf{GemOS}} $|$ \emph{C, x86, Operating Systems (CS330)}}{Aug 2019 -- Nov 2019}
      \resumeItemListStart
        \resumeItemPlain{Implemented mmap, munmap, mprotect with lazy allocation and pagefault handling; cfork/vfork with copy-on-write.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\href{https://github.com/shivamkm/machine-learning}{\textbf{Machine Learning}} $|$ \emph{Python, Keras, ML (CS771)}}{Aug 2019 -- Nov 2019}
      \resumeItemListStart
        \resumeItemPlain{CNN image classification using Keras; SGD for binary classification; multi-label Bonsai recommender system.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------RESEARCH-----------
\section{Research}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Data Race Detection for Task-Parallel Programs}{Jun 2019 -- Aug 2021}
      {Supervisor: Prof. Swarnendu Biswas, IIT Kanpur}{}
      \resumeItemListStart
        \resumeItemPlain{Designed novel algorithm \textbf{Tasker} integrating vector clocks with tree-based techniques; implemented using \textbf{LLVM} pass for memory instrumentation on task-parallel programs.}
        \resumeItemPlain{Achieved \textbf{1.48X speedup} over PTRacer baseline on 128GB Intel Xeon system with lower memory overhead.}
        \resumeItemPlain{\textit{``Efficient Data Race Detection of Structured Task Parallel Programs Using Vector Clocks''} --- S.~Kumar, A.~Agrawal, S.~Biswas $|$ Submitted to ISCGO 2022.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology, Kanpur}{CGPA: 9.4/10.0}
      {Bachelor of Technology in Computer Science and Engineering}{2017 -- 2021}
  \resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{Achievements \& Leadership}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{RockStar Award}, Microsoft ('22, '23) for exceptional contributions $|$ \textbf{Academic Excellence Award} ($\times$2), IIT Kanpur \\
      JEE Advanced \textbf{AIR 715} $|$ JEE Mains \textbf{AIR 348} $|$ KVPY Scholar $|$ NSE Physics \textbf{Top 1\%} $|$ Ram Prakash Chopra Scholarship \\
      Academic Mentor, IIT Kanpur ('18-19) $|$ Secretary, Dramatics Club, IIT Kanpur ('18-19)
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
