%-------------------------
% Resume in LaTeX - Shubham Kumar
% Based on: https://github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[a4paper,11pt]{extarticle}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure PDF is machine readable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small #1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small #1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItemPlain{#1}\vspace{-4pt}}

\newcommand{\resumeItemPlain}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Shubham Kumar} \\ \vspace{2pt}
    \small B.Tech Computer Science Engineering (3rd Year) \\ \vspace{2pt}
    \href{tel:+917870841473}{7870841473} \,$\vcenter{\hbox{\footnotesize\faMobile}}$
    $|$
    \href{mailto:shubhamkm07@gmail.com}{shubhamkm07@gmail.com} \,$\vcenter{\hbox{\footnotesize\faEnvelope}}$
    $|$
    \href{https://www.linkedin.com/in/shubham-kumar-05a9a5285}{linkedin.com/in/shubham-kumar} \,$\vcenter{\hbox{\footnotesize\faLinkedin}}$
    $|$
    \href{https://github.com/myselfshubham1}{github.com/myselfshubham1} \,$\vcenter{\hbox{\footnotesize\faGithub}}$
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {ITM University}{CGPA: 8.3/10.0}
      {B.Tech -- Computer Science Engineering}{2023 -- 2027}
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C, C++, Java, Python, SQL} \\
     \textbf{Core CS}{: Data Structures \& Algorithms, Object-Oriented Programming, DBMS, Operating Systems} \\
     \textbf{Backend / Systems}{: C++ STL, File Handling, MySQL, REST APIs, Postman} \\
     \textbf{AI / ML}{: NumPy, Pandas, Scikit-learn, YOLOv8, OpenCV} \\
     \textbf{Web}{: HTML, CSS, JavaScript}
    }}
 \end{itemize}

%-----------COURSEWORK-----------
\section{Relevant Coursework}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      Data Structures \& Algorithms $\cdot$
      Object-Oriented Programming $\cdot$
      Database Management Systems $\cdot$
      Operating Systems $\cdot$
      Computer Networks $\cdot$
      Software Engineering $\cdot$
      Discrete Mathematics $\cdot$
      Machine Learning
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Development Intern -- Blog Post Management System}{Industrial Training}
      {Intellige IT Studio}{Java, MySQL, REST APIs}
      \resumeItemListStart
        \resumeItemPlain{Completed industry-oriented software development training and developed a fully functional \textbf{Blog Post Management System} using Java, MySQL, HTML, CSS, REST APIs, and Postman.}
        \resumeItemPlain{Designed and implemented \textbf{REST-based backend APIs} for blog and user management supporting full CRUD operations (create, update, search, delete).}
        \resumeItemPlain{Implemented \textbf{User and Admin roles} with role-based access control for secure content management.}
        \resumeItemPlain{Enabled tracking of creation and update timestamps for blogs, ensuring data audit capabilities.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{MCP Server -- AI-Driven 3D Model Generation} $|$ \emph{Python, Socket Programming, Blender, Cursor AI}}{}
      \resumeItemListStart
        \resumeItemPlain{Designed and implemented a \textbf{custom MCP server} using socket-based communication for real-time tool integration.}
        \resumeItemPlain{Integrated \textbf{Blender \& Cursor AI} to enable 3D object generation using natural language prompts.}
        \resumeItemPlain{Built a \textbf{scalable, real-time system} capable of connecting multiple tools simultaneously.}
        \resumeItemPlain{Enabled full \textbf{customization and modification} of 3D models based on user input.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Object Detection using YOLOv8} $|$ \emph{Python, YOLOv8, OpenCV}}{}
      \resumeItemListStart
        \resumeItemPlain{Developed a \textbf{real-time object detection system} using the YOLOv8 deep learning framework.}
        \resumeItemPlain{Trained and evaluated the model on a dataset of \textbf{$\sim$10,000 images} to improve detection accuracy.}
        \resumeItemPlain{Implemented \textbf{live camera-based detection} with high accuracy for real-world applications.}
        \resumeItemPlain{Applied data preprocessing and model tuning techniques to optimize performance.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------MINI PROJECTS-----------
\section{Mini Projects}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{To-Do Application} -- Full-stack task management app with CRUD functionality \\
      \textbf{Chatbot} -- Interactive conversational bot using rule-based/NLP techniques \\
      \textbf{Calculator} -- Multi-function calculator application with scientific operations \\
      \textbf{Profile Calculator} -- Profile analytics and scoring tool \\
      \textbf{Number Guessing Game} -- Interactive CLI game with randomized logic and difficulty levels
    }}
 \end{itemize}

%-----------ACHIEVEMENTS-----------
\section{Achievements \& Hackathons}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      $\vcenter{\hbox{\tiny$\bullet$}}$ \textbf{Winner} -- Hackathon conducted by ITM University \\
      $\vcenter{\hbox{\tiny$\bullet$}}$ \textbf{Finalist} -- ``FinShield'' Hackathon conducted by Bank of India; presented solution at IIT Hyderabad \\
      $\vcenter{\hbox{\tiny$\bullet$}}$ \textbf{Participant} -- Smart India Hackathon (SIH) and actively participated in multiple inter-college hackathons
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
