%-------------------------
% Shivam Kumar Resume
%-------------------------

\documentclass[a4paper,9pt]{extarticle}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[empty]{fullpage}
\usepackage{charter}
\usepackage[usenames,dvipsnames]{color}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{tabularx}
\input{glyphtounicode}

\pdfgentounicode=1

\definecolor{accent}{rgb}{0.09,0.29,0.49}
\definecolor{textgray}{rgb}{0.20,0.20,0.20}
\definecolor{rulegray}{rgb}{0.72,0.78,0.84}

\hypersetup{
  colorlinks=true,
  urlcolor=accent,
  linkcolor=accent
}

\pagestyle{empty}
\addtolength{\oddsidemargin}{-0.44in}
\addtolength{\evensidemargin}{-0.44in}
\addtolength{\textwidth}{0.88in}
\addtolength{\topmargin}{-0.62in}
\addtolength{\textheight}{1.26in}
\setlength{\parindent}{0pt}
\setlength{\tabcolsep}{0pt}
\setlength{\emergencystretch}{2em}
\raggedbottom
\raggedright
\urlstyle{same}

\newcommand{\resumeTextSpacing}{\setlength{\baselineskip}{11.0pt}\spaceskip=0.34em plus 0.08em minus 0.03em\xspaceskip=0.45em plus 0.10em minus 0.04em}

\titleformat{\section}
  {\color{accent}\large\bfseries}
  {}
  {0pt}
  {\MakeUppercase}
  [\vspace{1pt}\color{rulegray}\titlerule]
\titlespacing*{\section}{0pt}{6pt}{4pt}

\newcommand{\contactSep}{\hspace{0.5em}{\color{rulegray}|}\hspace{0.5em}}
\newcommand{\projectLink}[2]{\href{#1}{\textcolor{textgray}{#2}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{2pt}
  \begin{tabularx}{\textwidth}{@{}Xr@{}}
    \textbf{\color{textgray}#1} & \textbf{\small #2} \\
    {\small\textit{#3}} & {\small\textit{#4}} \\
  \end{tabularx}
  \vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[3]{
  \vspace{2pt}
  \begin{tabularx}{\textwidth}{@{}Xr@{}}
    \textbf{\color{textgray}#1} & \textbf{\small #2} \\[1pt]
    \multicolumn{2}{@{}p{\textwidth}@{}}{\resumeTextSpacing #3} \\
  \end{tabularx}
  \vspace{-2pt}
}

\newcommand{\resumeItemPlain}[1]{\item #1}

\newenvironment{resumeItemList}{
  \begin{itemize}[
    leftmargin=0.18in,
    label={\color{accent}\bfseries--},
    itemsep=0.4pt,
    topsep=1.0pt,
    parsep=0pt,
    partopsep=0pt
  ]\resumeTextSpacing
}{
  \end{itemize}\vspace{0pt}
}

\newcommand{\skillrow}[2]{
  \textbf{#1} & \hspace{0.35em}#2 \\
}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
  {\Huge\bfseries\color{accent} Shivam Kumar}\\[5pt]
  \small
  \href{tel:+919129085031}{+91-9129085031}
  \contactSep
  \href{mailto:shivamkm07@gmail.com}{shivamkm07@gmail.com}
  \contactSep
  \href{https://www.linkedin.com/in/shivamkm07}{linkedin.com/in/shivamkm07}
  \contactSep
  \href{https://github.com/shivamkm07}{github.com/shivamkm07}
\end{center}
\vspace{-3pt}

%-----------SUMMARY-----------
\section{Summary}
\resumeTextSpacing
SDE II at Microsoft building Azure cloud-native platforms, distributed systems, and Kubernetes-based container infrastructure. Expertise in microservices architecture, AI/LLM-powered SRE automation, and Dapr (CNCF Graduated). IIT Kanpur, 5 YoE.

%-----------EXPERIENCE-----------
\section{Experience}

\resumeSubheading
  {Software Development Engineer II}{Jul 2024 -- Present}
  {Microsoft -- Azure Container Apps}{Hyderabad, India}
\begin{resumeItemList}
  \resumeItemPlain{Engineered AI-powered SRE agent for Azure Container Apps, reducing P50 TTM by \textbf{97\%} and TTR by \textbf{64\%}; added RCA subagents, self-repair, auto-resolution, and Ev2 deployment pipelines.}
  \resumeItemPlain{Enhanced Azure Functions on ACA with support for graceful drain, secure key management, KEDA scale-rule customization, JWT clock-skew tolerance, invocation tracing, and durable events logging; deployed to \textbf{\textasciitilde{}1,322} apps.}
  \resumeItemPlain{Contributed to ACA Express Public Preview on Azure Dev Compute (ADC), resolving P0 blockers for ephemeral volumes and Log Analytics customer logs; unblocked \textbf{\textasciitilde{}100K+} ACA environments.}
  \resumeItemPlain{Implemented ACA Sessions management APIs and fixed critical async execution bugs for \textbf{\textasciitilde{}300} external customers; enabled early Fabric session deletion to reduce resource cost.}
  \resumeItemPlain{Led Dapr AKS Extension rollouts (v1.15, v1.16), remediating CVEs across \textbf{\textasciitilde{}400} AKS clusters and integrating CodeQL scanning for enhanced security posture.}
  \resumeItemPlain{Integrated ACA agentic apps with Foundry Control Plane (FCP), supporting declared and auto-detected agents and central management for \textbf{\textasciitilde{}2,000+} applications.}
\end{resumeItemList}

\resumeSubheading
  {Software Development Engineer I}{Jul 2021 -- Jul 2024}
  {Microsoft -- Dapr}{Hyderabad, India}
\begin{resumeItemList}
  \resumeItemPlain{Stabilized Dapr building blocks across Configuration API, MQTT PubSub, CosmosDB state and Redis/PostgreSQL config stores. Added support for Event Hubs bulk-subscribe and CLI airgap install.}
  \resumeItemPlain{Implemented Cascade Terminate/Purge for Dapr Workflows and fixed scalability bottlenecks found through performance tests.}
  \resumeItemPlain{Co-launched ACA Sessions, owning Node.js/.NET code-interpreter support for Security Copilot; fixed critical bugs and added regression coverage for \textbf{3000+} active sessionPools.}
  \resumeItemPlain{Designed patch-based internal fork infrastructure across \textbf{5} Dapr repositories; built OneBranch/Ev2 pipelines and automated OSS-to-internal releases with \textbf{<1} day SLA.}
  \resumeItemPlain{Delivered multi-architecture Dapr/dashboard images, 1P Container Registry migration, ACA nightly builds, and Mariner/distroless images to MCR.}
\end{resumeItemList}

\resumeSubheading
  {Quantitative Research Intern}{May 2020 -- Jul 2020}
  {JP Morgan \& Chase -- E-Trading}{Mumbai, India (Remote)}
\begin{resumeItemList}
  \resumeItemPlain{Built price prediction models using \textbf{LSTM}, feedforward neural networks, and regression with univariate feature selection; improved predictive power by \textbf{40\%} for HK names through feature standardization.}
  % \resumeItemPlain{Implemented L1 and L2 features for optimizing model parameterization across multiple asset classes.}
\end{resumeItemList}

%-----------RESEARCH-----------
\section{Research}
\resumeSubheading
  {Data Race Detection for Task-Parallel Programs}{Jun 2019 -- Aug 2021}
  {Supervisor: Prof. Swarnendu Biswas, IIT Kanpur}{}
\begin{resumeItemList}
  \resumeItemPlain{Designed \textbf{Tasker}, combining vector clocks with tree-based techniques; built an \textbf{LLVM} memory instrumentation pass and achieved \textbf{1.48x speedup} over PTRacer with lower memory overhead.}
  \resumeItemPlain{\textit{``Efficient Data Race Detection of Structured Task Parallel Programs Using Vector Clocks''} --- S.~Kumar, A.~Agrawal, S.~Biswas \textbar{} Submitted to ISCGO 2022.}
\end{resumeItemList}

%-----------PROJECTS-----------
\section{Projects}
\resumeProjectHeading
  {\projectLink{https://github.com/shivamkm07/gemOS}{GemOS} \textbar{} \emph{C, x86 -- OS kernel (IIT Kanpur CS330)}}{Aug 2019 -- Nov 2019}
  {Implemented mmap/munmap/mprotect with lazy allocation and page-fault handling; cfork/vfork with copy-on-write semantics.}
\resumeProjectHeading
  {\projectLink{https://github.com/shivamkm/decipher}{Cipher Decoder} \textbar{} \emph{Python, Modern Cryptology (CS641)}}{Aug 2020 -- Nov 2020}
  {Performed differential cryptanalysis of 3-DES and decrypted Caesar/Vigenere ciphers using frequency analysis.}

%-----------EDUCATION-----------
\section{Education}
\resumeSubheading
  {Indian Institute of Technology, Kanpur}{CGPA: 9.4/10.0}
  {Bachelor of Technology in Computer Science and Engineering}{2017 -- 2021}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\fontsize{9.4}{10.2}\selectfont\resumeTextSpacing
\begin{tabularx}{\textwidth}{@{}p{1.85in}X@{}}
  \skillrow{Languages:}{Go, C\#/.NET, Python, C/C++}
  \skillrow{Cloud \& Infra:}{Azure (ACA, Functions, AKS), Kubernetes, Docker, Helm, KEDA}
  \skillrow{Distributed Systems:}{Dapr (CNCF), Microservices, Service Mesh, gRPC, Pub/Sub}
\end{tabularx}

%-----------ACHIEVEMENTS-----------
\section{Achievements \& Recognition}
\begingroup
\fontsize{9.4}{10.2}\selectfont\resumeTextSpacing
\begin{resumeItemList}
  \resumeItemPlain{\textbf{IDC Pinnacle FY'26 -- Best AI Success Story} (ACA RCA Agent squad, \textasciitilde{}200+ competing teams); \textbf{RockStar Award}, Microsoft ('22, '23).}
  \resumeItemPlain{\textbf{Academic Excellence Award} (x2), IIT Kanpur \textbar{} JEE Adv. \textbf{AIR 715} \textbar{} JEE Main \textbf{AIR 348} \textbar{} KVPY Scholar \textbar{} NSE Physics \textbf{Top 1\%}.}
\end{resumeItemList}
\endgroup

%-------------------------------------------
\end{document}
